Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\section{Conclusion \& Future Works}
The implemented performance regression analysis system can detect and analyse the cause of regression on Microservice-based application using Kolmogorov-Smirnov test and Critical Path analysis. However, the Kolmogorov-Smirnov test alone cannot determine exactly whether the detected regression is caused by internal or external factors, therefore the Critical Path analysis is required to help determine the exact cause of the regression.

>>>>

\section{Conclusion \& Future Works}
The implemented performance regression analysis system can detect and analyze the cause of regression on Microservice-based application using Kolmogorov-Smirnov test and Critical Path analysis. However, the Kolmogorov-Smirnov test alone cannot determine exactly whether the detected regression is caused by internal or external factors, therefore the Critical Path analysis is required to help determine the exact cause of the regression.
